Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
small changes

\documentclass[10pt,conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[nocompress]{cite}
\usepackage{caption}
\usepackage{subcaption}

@@

If the probe or retransmission is lost, as shown 
in Figure~\ref{tcpf}, then TLP performs better than RTO retransmission as it waits for one 
probe timeout and one RTO experiation instead of two RTO expirations, thus avoiding the exponential backoff of the RTO.

>>>>

\documentclass[10pt,conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[nocompress]{cite}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{balance}

@@

If the probe or retransmission is lost, as shown 
in Figure~\ref{t1pp}, then TLP performs better than RTO retransmission as it waits for one 
probe timeout and one RTO expiration instead of two RTO expirations, thus avoiding the exponential backoff of the RTO.
